A seamless, client-centric programming model for type safe web applications

### 2014-05-12 paper.tex
ServerDummy -> return ServerDummy
pass add -main-is -> add -main-is

To run this example, an address and a port must be provided so that the client
knows which server to contact. There are several ways of doing this:
using the GHC plugin system, through Template Haskell or by slightly altering
how program entry points are treated in a compiler or wrapper script, to name
a few. A non-intrusive method when using the GHC/Haste compiler pair would
be to pass add \lstinline!-main-is setup! to both compilers' command line
and add the \lstinline!setup! function to the source code.

@@

\begin{code}
liftServerIO :: IO a -> App (Server a)
liftServerIO _ = App ServerDummy
\end{code}

>>>>

To run this example, an address and a port must be provided so that the client
knows which server to contact. There are several ways of doing this:
using the GHC plugin system, through Template Haskell or by slightly altering
how program entry points are treated in a compiler or wrapper script, to name
a few. A non-intrusive method when using the GHC/Haste compiler pair would
be to add \lstinline!-main-is setup! to both compilers' command line
and add the \lstinline!setup! function to the source code.

@@

\begin{code}
liftServerIO :: IO a -> App (Server a)
liftServerIO _ = App $ return ServerDummy
\end{code}
